---
title: "886_assignment2_Q3"
author: '44414161'
date: "05/09/2019"
output:
  word_document: default
  html_document: default
---

### Qestion 3

#### 5.7

```{r}
age1<-seq(70,75,1)
Ecx<-c(1000,1005,1010,1008,1006,998)
dx1<-c(80,90,95,105,115,125)
mux<-dx1/Ecx

```

Set the likelihood function. Conduct the linear regression for the logarithm of force of mortality and the logarithm of age to find the coefficients as our initial values. Find the solution of b and c as the function is maximised. 
Then inplug estimate b and c into the Gompertz formulae to find graduated estimates of force of mortality.


```{r}
likelh<-function(p){-prod(exp(-Ecx*p[1]*p[2]^age1)*(Ecx*p[1]*p[2]^age1)^dx1/factorial(dx1))}
logmux<-log(mux)
mod.1=lm(logmux~age1)
mod.1$coefficients
iv1<-c(exp(-8.67324637),exp(0.08788271))
iv1
```


```{r}
nlm(likelh,iv1)
b1<-nlm(likelh,iv1)$estimate[1]
c1<-nlm(likelh,iv1)$estimate[2]
Est1<-b1*c1^age1
grad1<-data.frame(age1,mux,Est1)
grad1
```



#### 5.8
Set the least square function by using Ex as weights. Conduct the linear regression to find the coefficients as our initial values. Find the solution of b and c as the function is minimised. 
Then inplug estimate b and c into the mathematical formulae to find graduated estimates of mortality rate.


```{r}
age2<-c(30:49)
Ex2<-c(70000,66672,68375,65420,61779,66091,68514,69560,65000,66279,
      67300,65368,65391,62917,66537,62302,62145,63856,61097,61110)
dx2<-c(39,43,34,31,23,50,48,43,48,47,
      62,63,84,86,120,121,122,162,151,184)
qx2<-dx2/Ex2
logqx2<-log(qx2/(1-qx2))
wls2<-function(p){sum(Ex2*(logqx2-p[1]-p[2]*age2)^2)}
mod.2<-lm(logqx2~age2)
mod.2$coefficients
iv2<-c(-10.862882,0.1002807)
nlm(wls2,iv2)
b2<-nlm(wls2,iv2)$estimate[1]
c2<-nlm(wls2,iv2)$estimate[2]
Est2<-exp(b2+c2*age2)/(1+exp(b2+c2*age2))
grad2<-data.frame(age2,qx2,Est2)
grad2
```

#### 5.9
Set the least square function by using Ex as weights. Conduct the linear regression to find the coefficients as our initial values. Find the solution of b and c as the function is minimised. 
Then inplug estimate a and b into the mathematical formulae to find graduated estimates of mortality rate.
```{r}
age3<-c(47:67)
Ex3<-c(166,187,218,243,276,302,347,390,430,494,558,628,701,813,917,1040,1182,1299,1432,1596,1752)
dx3<-c(2,2,4,6,2,4,7,3,9,9,8,11,14,18,18,24,30,43,41,54,64)
qx3<-dx3/Ex3
qs3<-c(0.00505,0.00570,0.00644,0.00728,0.00826,0.00930,0.01051,0.01184,0.01331,0.01492,0.01668,0.01859,0.02065,0.02287,0.02525,0.02778,0.03049,0.03339,0.03648,0.03978,0.04332)

wls3<-function(p){sum(Ex3*(qx3-p[1]-p[2]*qs3)^2)}
mod.3=lm(qx3~qs3)
mod.3
iv3<-c(0.009279,0.570217)
nlm(wls3,iv3)
a3<-nlm(wls3,iv3)$estimate[1]
b3<-nlm(wls3,iv3)$estimate[2]
Est3<-a3+b3*qs3
grad3<-data.frame(age3,qx3,Est3)
grad3

```

