---
title: "886_assignment 2_Q2"
author: '44414161'
date: "05/09/2019"
output:
  word_document: default
  html_document: default
---
### Qestion 2

```{r}
Ex<-c(15518,19428,21594,21890,19174,15775,11414,6993,3276,1096,201)
ax<-c(65,144,219,378,465,557,685,644,471,217,67)
ex<-c(73.9,134.6,223.9,346.3,468.1,600.2,675.5,637.4,458.7,240.6,61.4)
qx<-ex/Ex
var<-ex*(1-qx)
zx<-(ax-ex)/sqrt(var)
```


#### Chi Square Test
$$\sum_{allages}{z_x^2}$$

we can use chi square test to check adherence of data. The degree of freedom is 10.
The chi square test statistic is smaller than 95th percentile of the chi square distribution, the null htpothesis is not rejected and adherence to data is good. 

```{r}
chiStat<-sum(zx^2)
chiStat
df1<-length(zx-1)
qchisq(0.95,df1)


```

Howerver, this test does not detect the case where there are a few large diviation offset by small deviations.


#### Standardised Deviations Test
The standardised deviation test deviation test statistic is :
$$\sum_{allages}\frac{(A-E)^2}E$$
The degree of freedom is 3. The test statitic is smaller than $\chi^2_n(0.95)$, so the adherence to data is good.


```{r}
z<-data.frame(zx)

A1<-length(z[z$zx<(-1),])
A2<-length(z[z$zx>(-1)&z$zx<0,])
A3<-length(z[z$zx>0&z$zx<1,])
A4<-length(z[z$zx>1,])
A<-c(A1,A2,A3,A4)

E1<-pnorm(-1,0,1)*11
E2<-(pnorm(0,0,1)-pnorm(-1,0,1))*11
E3<-(pnorm(1,0,1)-pnorm(0,0,1))*11
E4<-(1-pnorm(1,0,1))*11
E<-c(E1,E2,E3,E4)

sd<-sum((A-E)^2/E)
sd
qchisq(0.95,3)
```

#### Cumulative Deviation Test
The test statistic is:
$$\frac{\sum_x(d_x-Exq_x)}{\sqrt{\sum_x{Exqx(1-q_x)}}}$$
And it is smaller than the 1.96, it is approximately normally distributed and the adherence to data is satisfactory. 
```{r}
cd<-sum(ax-ex)/sqrt(sum(var))
cd
```

#### Sign Test
Under our assumption, there should be equal numbers of positive and negative deviations so we should do further signs test.
The signs test statistic is the number of positive $z_x$'s.It is 6 which is greater than k, so the gradusted estimates are not too low and vice versa compared to the data.
```{r}
k=qbinom(0.025,11,0.5)
k
n1=length(z[z$zx>0,])
n1
```

```{r}
n=length(zx)
s=0
cdf<-numeric(n)

for(i in 1:n){
  s=s+choose(n,i)*0.5^11
  cdf[i]<-s
}
k<-c(1:11)
data.frame(k,cdf)

```

#### Grouping of Signs Test
The grouping of the signs test statistic is the number of distinct roups of positive $z_x$'s. It is 4 which is bigger than k so the adherence to data is good.

```{r}
n2=length(z[z$zx<0,])
s1=0
cdf<-numeric(n1)

for(i in 1:n1){
  s1<-s1+choose(n1-1,i-1)*choose(n2+1,i)/choose(n,n1)
  cdf[i]<-s1
}
k<-c(1:6)
data.frame(k,cdf)
```

##### Serial Correlation Test
The test statistic is smaller than 1.64 so the adherence to the data is good.
```{r}
z_1<-z[-n,]
z_2<-z[-1,]
zbar1<-sum(z_1)/(n-1)
zbar2<-sum(z_2)/(n-1)
sc<-sum((z_1-zbar1)*(z_2-zbar2))*sqrt(n-1)/sqrt(sum((z_1-zbar1)^2)*sum((z_2-zbar2)^2))
sc  #< 1.64
```

In conclusion, the fidelity to data is good.